### 2020-10-20 submission/manuscript.Rmd
Create Figures 3 and S4

otu_cov_bc <- r_cov_bc %>% filter(method == "otu") %>% arrange(cv_diff) %>% slice(1, nrow(.)) %>% pull(cv_diff)

**How do the relationships between communities change when they are screened by removing rare ASVs.** Considering the loss of the number of ASVs, diversity, and information when a community has its rarest ASVs removed, it seemed likely that the relationship between communities would be altered. To assess the impact of removing rare ASVs on measures of alpha diversity between samples I calculated the coefficients of variation (COV, i.e. standard deviation divided by the mean) for the number of ASVs and diversity for each study at multiple abundance thresholds. The COV for the number of ASVs across the studies after removing singletons were between `r oxford_comma(pc_cov_sobs, 1)`-times larger than they were without removing singleton ASVs. Similarly, the COVs for the diversity of ASVs were between `r oxford_comma(pc_cov_shannon, 1)`-times larger when singletons were removed than when they were not removed.To assess the impact of removing rare ASVs on measures of beta diversity between samples I calculated the COV of the Bray-Curtis distances between samples within the same study at multiple abundance thresholds. The COV between Bray-Curtis distances within a study when singletons were removed was between `r oxford_comma(pc_cov_bc, 1)`-times larger than when they were not removed. Increasing the minimum abundance threshold increased the COV between samples when using metrics of alpha and beta diversity. When ASVs were clustered into OTUs the difference in the COV was less than it was for the ASVs (**Figure 2**). These results indicate that removing rare ASVs increases the dissimilarity between samples, which could have a significant impact on the statistical power to detect differences between treatment groups.

>>>>

otu_cov_bc <- r_cov_bc %>% filter(method == "otu") %>% arrange(cv_diff) %>% slice(1, nrow(.)) %>% pull(cv_diff)
```

**How do the relationships between communities change when they are screened by removing rare ASVs.** Considering the loss of the number of ASVs, diversity, and information when a community has its rarest ASVs removed, it seemed likely that the relationship between communities would be altered. To assess the impact of removing rare ASVs on measures of alpha diversity between samples I calculated the coefficients of variation (COV, i.e. standard deviation divided by the mean) for the number of ASVs and diversity for each study at multiple abundance thresholds. The COV for the number of ASVs across the studies after removing singletons were between `r oxford_comma(pc_cov_sobs, 1)`-times larger than they were without removing singleton ASVs (Figure 3A). Similarly, the COVs for the diversity of ASVs were between `r oxford_comma(pc_cov_shannon, 1)`-times larger when singletons were removed than when they were not removed (Figure 3B). To assess the impact of removing rare ASVs on measures of beta diversity between samples I calculated the COV of the Bray-Curtis distances between samples within the same study at multiple abundance thresholds. The COV between Bray-Curtis distances within a study when singletons were removed was between `r oxford_comma(pc_cov_bc, 1)`-times larger than when they were not removed (Figure 3C). Increasing the minimum abundance threshold increased the COV between samples when using metrics of alpha and beta diversity. When ASVs were clustered into OTUs the difference in the COV was less than it was for the ASVs (Figure S4). These results indicate that removing rare ASVs increases the dissimilarity between samples, which could have a significant impact on the statistical power to detect differences between treatment groups.
